Optimal Tetrahelices Transforming between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix

### 2018-03-08 r1doc/RebuttalTetrahelixUntwistV2.tex

The inradius of the tetrahelix was also calculated to consider the insertion of material inside the
tetrahelix.

The equitetrabeam is introduced as a special case that the rail angle is zero. It is proposed that
transformation from tetrahelix to equitetrabeam is possible by changing the minimax ratio about
16\%.

Overall, this paper is acceptable, but requires some revision. The following includes some comments.

\subsection{Modification}
\begin{itemize}
\item
The sentences of this paper need to be compact. Please read several times and then clean
the sentences.
``without loss of generality'' $\rightarrow$ ``generally''
\highlighttext{The term ``without loss of generality'' is being used specifically as mathematical jargon\cite{wiki:wolog} to represent an assumption allowed in proof because of symmetry or an ability to make
  a choice that does not change the validity of the proof.
  However, because this was unclear to the reviewer, in order to clarify this, I have added the word ``assume'' to the first use of the phrase ``without loss of generality'' and the phrase ``By symmetry'' to the second use.
  }

\highlighttext{TODO: reread looking for additional ways to make sentences more compact.}
\item
  The explantaion for figure 8 can be erased by drawing the general case for figure 8.
  \item
    Instead of sentence starting to ‘we……’ , the passive sentence is recommended.
    \highlighttext{
      I believe editorial opinon is somewhat divided on the use of the word ``we'' when it is used to mean ``the author and the reader togheter'' as I have used it. Most editors do not prefer passive sentences in general.
      Nonetheless, in deference to the reviewer, I have searched the paper for each use of the ``we'' and
      removed it in most, but not all cases.
      }
    \item 
 The following sentence is obscure. You’d better suggest a way to measure optimality using
 some kinematic indices :
\begin{quote}
 We have not yet proved that a two-class tetrahelix is optimal, but it suffices to show
that there exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
\end{quote}

\highlighttext{
  The reviewer has generally noted that I may not have motivated my definition of ``optimality''
  strongly enough. To improve this, I have made some changes:
... displays a continuum of tetrahelices optimal in a \bf{
  in the sense of being
as regular as possible},
which is the main result of this
paper.
}

\highlighttext{
  Additionally, in the section on Optimal Tetrahelices, I have inserted the following sentence which helps to
  explain the definition of optimality:
  \bf{By maintaining all lengths as close to the same ``regular'' length as possible,
such as the mean length of the actuator,
one retains the greatest possible freedom of motion for the robot.}
  }

\highlighttext{This specific sentence has been clarified to show that ``not yet proved'' means
  ``not yet reached the proof in this paper of that fact that'' by changing the sentence to refer
  to the next theorem:
  \begin{quote}
  We have not yet {\em
proved theorem 3 which asserts} that a two-class tetrahelix is optimal, but it suffices to show that there
exists such a better tetrahelix to show that different radii imply a suboptimal
tetrahelix.
  \end{quote}
  I unfortunately am not sure how to relate this notion of optimality to kinematic indexes, but
  have attempted elsewhere to clarify why this definition of optimality is valuable for
  Tetrobot-style robots.
  }
\item 
 It is recommended to change:
 ``conincident'' $\rightarrow$ ``coincident''
 \highlighttext{Corrected--an embarassing mistake in my spelling correction software.}
 \item
\item In page 3, after the eq. (4)
  In this formula, ``integral values of n'' $\rightarrow$ In this formula, ``integer values of n''
  \highlighttext{Corrected.}
  \item 
In eq. (23), need to be changed as

@@

\item 
- In page 8, the graph could not be observed through this following address,
https://github.com/PubInv/tetrahelix/blob/master/tetrahelix.nb . For user not using the
Mathematica, it is recommended to show the tendency of the graph of eq. (23) by setting
rail angle as 0, 15, and 30(deg).

\highlighttext{
  In order to make this clearer and avoid forcing the user to follow a link, I have included the graphic
  inline in the document with the following change to the relevant sentence:}

\begin{quote}

  By inspection of the graph of the derivative of this ratio rendered in \cref{fig:partialderivativediagram}
  observe that the partial derivative of this with respect to
radius $r$ is always negative, for any $\rho \leq \rho_{bc}$.

@@

\begin{figure}
     \centering
     \includegraphics[width=0.45\textwidth]{figures/PartialDerivativeDiagram.png}
     \caption{Partial Derivative against $\rho$ and $r$: $ \frac{\partial \frac{\text{two-hop}(r)}{ \text{one-hop}(r)}}{\partial \rho, r} $ }
  \label{fig:partialderivativediagram}
\end{figure}
\end{quote}

\item
  - In eq. (27) and (28), it needs to be changed as 9/2 instead of 9.
  \highlighttext{Corrected--thank you!}  
  \item
- Figure 12 interferes to understanding the related contents. It is recommended to change
figure 12 referring the following figure,

\highlighttext{The reviewer has provided an excellent simplifying diagram. I have created a diagram similar
  (see \cref{fig:projectiondiagram})
  to theirs but retaining the numbering features, which are useful in the first place the
  figure is referenced, and in explaining the derivation of the inradius.
  I thank the reviewer for this improvement.}

@@

  \item
    I think the explaining optimization part should be revised. For a certain optimization problem, I think mathematics definition or algorithmic explanation can be helpful to understand the problem quickly. I think the author should refer problem definition standards from other optimization papers to revise this.
    \highlighttext{
      In order to clarify the ``Optimal Tetrahelices are Triple Helices'' section as requested,
      I have provided a mathematical description of the optimization, and a more mathematical
      description of the definition of the tetrahelix.
      }

  \item    
    In my opinion, the problem definition and proof of theorems looks being done based on personal experiences. I recommend using mathematical derivation or expression if possible.
    \highlighttext{
      I believe the theorems are all true (and verified by computer experimentation) and that the proofs
      are rigorous. However, in deference to the reviewer I have attempted to express parts of them
      more formally in several places. Unfortunately, it is beyond my ability to make them more formal
      in the space allowed in this paper. I hope readers will find them convincing at the available length.
      }

  \item    
    I think the demonstration by experiment can be helpful to understand the idea. Video attachment is recommended.
    \highlighttext{
All math
developed here is available in JavaScript and demonstrated by an interactive
design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
\bf{and a video[9]},
from which figs. 1 and 2 and later figures in this paper 
are taken.      
      }

### 2018-03-08 r1doc/TetrahelixUntwistV2.tex
more updates

The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix) (see \cref{fig:closeup,fig:closeuporthog}), is
a face-to-face stack of tetrahedra that winds about a straight axis.
Architects, structural engineers, and roboticists are inspired
by and follow such regular mathematical models.
However, since they can also build structures and
machines from members of differing or even dynamically changing length, it is
useful to develop the mathematics of structures formed from tetrahedra
where we relax regularity.

@@

Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
a term now commonly used. In this paper, we reserve \emph{BC helix} to mean the purely
regular structure and use \emph{tetrahelix} to refer
to any structure isomorphic to the BC helix.

@@

Imagining \cref{fig:closeup} or \cref{fig:closeuporthog} as a static mechanical structure,
we can observe that it is useful to the mechanical engineer
because the structure is a mechanically strong, inherently rigid,
omni-triangulated space frame.
Then we can imagine that each static edge is replaced with an
actuator that can dynamically become shorter or longer in response to electronic control,
and the vertices are joints that support sufficient angular displacement
for this to be possible. An example of such a machine is a Tetrobot,
shown in \cref{fig:tetrobot}.

A BC helix does not rest stably on a plane. It is convenient to
be able to ``untwist'' it and to form a tetrahelix space frame that has a
flat planar surface. By making length changes in a certain way, we can
untwist a tetrahelix to form a \emph{tetrabeam} which has planar faces
and has, for example, an equilateral triangular profile. This paper
develops the equations needed to untwist the tetrahelix. All math
developed here is available in JavaScript and demonstrated by an interactive
design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
\highlighttext{and a video\cite{readvideo}},
from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
are taken.

@@

\Cref{fig:series} displays a continuum of tetrahelices optimal in a certain sense,
which is the main result of this
paper. The closest helix is the BC helix, and the furthest
is the equitetrabeam, defined in \cref{sec:equitetrabeam} and \cref{fig:naming,fig:equitetrabeam}.

@@

However, a robot must move, and so it is interesting to consider the
transmutations of these regular geometries. Developing a functional
gait for our physical Tetrobot (the 7-Tet Glussbot) was in fact the motivation
for this work.
By changing only the length of only one third of the members,
we can dynamically untwist a physical Tetrobot
forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane,
as shown in \cref{fig:tetrobot}.

By untwisting the tetrahelix so that is has a planar surface resting on the ground,
we may consider each vertex touching the ground a foot or pseudopod. A robot can thus
become a hexapod or $n$-pod Tetrobot, and the already well-developed approaches to
hexapod gaits may be applied to make the robot walk or crawl.

@@

\highlighttext{
The remainder of this  paper:
\begin{enumerate}
\item Provides a new formulation for the BC helix that is more natural for engineers,
\item Defines a concept of minimum maximum edge-length optimality and proves that all
    optimal tetrahelices are in fact triple helices,
\item Provides formulae for construct optimal tetrahelices of different twists or for optimally
    transforming a
    robot from a twisted to a planar configuration,
\item Gives a formula for the inradius of an optimal tetrahelix,
\item Describes a completely planar tetrahlix (the \emph{equitetrabeam} useful as a structural beam or for apply standard robot gaits to a tetrahedral robot, and
\item Discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
\end{enumerate}
}

@@

We would like to design nearly regular tetrahelices with a formula that
gives the vertices in space. Eventually, we would like to design them
by choosing the lengths of a small set of members.
In a space frame, this is a static design choice; in a Tetrobot, it is a
dynamic choice that can be used to twist the robot and/or exert linear or
angular force on the environment.

Ideally, we would have a simple formula for defining the vertices based on
any curvature or pitch we choose. It is a goal of
this paper to relate the Cartesian coordinate approach and the member-length approach to
generating a tetrahelix continuum.

H.S.M Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and
translation of the tetrahedra by showing the
rotation is:
\begin{equation}
\theta_{bc} = \arccos(-2/3) 
\end{equation}
and the translation:
\begin{equation}
h_{bc} = 1/\sqrt{10}.
\end{equation}

@@

This formula defines a helix, but it is not any of the apparent helices, or \emph{rail} helices, of the
BC helix, but rather one that winds much more rapidly through all
vertices. To a designer of tetrahelices, it is more natural to think of
the three helices which are visually apparent, that is, those three
which are closely approximated by the outer edges or rails of
the BC helix. We think of each of these three rails as being a different color: red, blue, or yellow.
This situation is illustrated in \cref{fig:helixcomparison}, wherein the black helix represents that
generated by \cref{graycoxeter},
and the colored helices are generated by \cref{eq:colored}, below.

In order to develop the continuum of slightly irregular tetrahelices,
we need a formula that gives us the vertices of just
one rail helix, denoted by color $c$ and integer vertex number $n$:
\[
(\forall n \in \mathbb{Z}, \forall c \in \{0,1,2\} : \vec{H}_{BCcolored}(n,c) = \vec{V}(3n +c)) .
\]

@@

Note, in \cref{railanglefig}, the $z$-axis travel for one rail edge is denoted by $d$. In \cref{graycoxeter} and  \cref{eq:colored}, the variable
$h$ is used for one third of the distance, we name $d$. We will later justify that $d = 3h$.
In this paper, we assume the length of a rail
is always $1$ as a simplification, except in proofs concerning rail length.
We make the rail length a parameter in our JavaScript code in
\url{https://github.com/PubInv/tetrahelix/blob/master/js/tetrahelix_math.js} \cite{readtetrahelix}.

The $\vec{H}_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho_{bc}$ rather than $\theta_{bc}$.
Intuitively, we seek an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$.
We expand 
the expressions $\theta_{bc}$ and $\rho_{bc}$ in \cref{eq:colored} and seek to isolate the term $c 2\pi/3 $.

@@

Thus, starting with the expression:
\begin{align*}
  c \theta_{bc} 
\end{align*}
we introduce 3 into the denominator...
\begin{align*}
  (c/3)  (3 \theta_{bc}) 
\end{align*}
we want $2\pi$ in numerator, so add canceling terms...
\begin{align*}
  (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) 
\end{align*}
...and then use the definition of $\rho_{bc}$
\begin{align*}
  (c / 3) \rho_{bc}  + c 2 \pi /3 
\end{align*}
finally we obtain:
\begin{equation}
  c  ( \rho_{bc} +  2 \pi) /3  \text{.}
\end{equation}

@@

Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued).
We can now assert that in \cref{fig:helixcomparison} the black helix winds at
$\frac{3 \theta_{bc}}{\rho_{bc}} \approx 11.16 $ times the rate of a rail helix.

From this formulation it is easy to see that moving one vertex on a rail
($\vec{H}_{BCcolored}(n,c)$ to $\vec{H}_{BCcolored}(n+1,c)$ for any $n$ and $c$)
moves us $\rho_{bc}$ radians around a circle. Since:
$ \frac{2 \pi}{\rho_{bc}} \approx 10.16 $
we can see that there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a
complete revolution of the tetrahelix.

@@

The pitch is less than the number of tetrahedra because the tetrahedra
edges are not parallel to the axis of the tetrahelix.  It is a famous and interesting result
that the pitch is irrational. A BC helix never has two tetrahedra at
precisely the same orientation around the $z$-axis. However, this is
inconvenient to designers, who might prefer a rational pitch.
The idea of developing a rational period by arranging solid tetrahedra by relaxing
the face-to-face matching
has been explored\cite{sadler2013periodic}. 
We develop, below, slightly irregular edge lengths that support, for example,
a pitch of precisely 12
tetrahedra in one revolution which would allow an architect to
design a pleasing column having the top and bottom tetrahedra in the same relationship to the
viewer on both the capital and the basis.

@@

We use the term \emph{tetrahelix} to mean any structure physically constructible of
vertices and finite edges which is isomorphic to the BC helix and in which the
vertices lie on three helices.
By isomporphic we mean there is a one-to-one mapping between both
vertices and edges in the two tetrahelices.
One could consider various definitions of optimality for a
tetrahelix, but the most useful to us as roboticists working with the Tetrobot
concept is to minimize the
maximum ratio between any two edge lengths, because the Tetrobot uses
mechanical linear acutators with
limited range of extension.

A \emph{triple helix} is three congruent helices that share an axis. We show that
optimal tetrahelices are in fact triple helices with the same radius, so that all
vertices are on a cylinder. In stages, we demonstrate that the helices in optimal tetrahelices:
\begin{enumerate}
\item have the same pitch,
\item have parallel axes,
\item share the same axis,
\item have the same radius,
\item have the same rail length,
\item have axially equidistant vertices, and therefore
\item are in fact triple helices.
\end{enumerate}

Suppose that all three rails do not have the same pitch. If we start at any shortest edge between
two rails, as we move
from vertex to vertex away from our start edge, the edge lengths
between rails must always lengthen without bound,
which cannot be optimal.
So we are justified in talking about the
\emph{pitch} of 
the optimal tetrahelix as the pitch of its three rail helices, even though there are
three such helices of equivalent pitch.

Similarly, if the axes are not parallel, there is an edge of
unbounded length in the structure, so we do not consider such cases.

Define a \emph{minimax edge-length optimal tetrahelix} or just an
\emph{optimal tetrahelix} to be a tetrahelix for which there exists
no other tetrahelix with lower ratio of longest edge length to shortest edge length.

We wish to show that in an optimal tetrahelix, all vertices lie on the cylinder
of radius $r$, regardless of where they lie on the $z$-axis.

As a little lemma for the proof below, observe that a tetrahelix of zero radius, where
all points lie on the same line,
is not as optimal as a tetrahelix of a small radius. The edges between rails will be
shorter than the rail edges, and moving them apart slightly lengthens the between-edge
rails, improving the ratios.

In the proof, below, we find it useful to consider projection diagrams that are the axial projection
of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram,fig:wobble} are examples
of such a diagram.
\begin{lemma}
  If the rail angle $0 < \rho < \pi$ is a rational multiple of $\pi$, then the projection of
  edges in a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
  regular polygon of 3 or more sides, or else they fill in a complete circle.
  \label{lemma:ngon}
\end{lemma}
\begin{proof}
  All points lying on a helix projected along the axis lie on a circle in the $XY$-plane.
  Helices are periodic in the $z$ dimension modulo $2\pi$.
  If $2\pi/\rho$ is irrational, the projection onto the $XY$-plane will contain
  an unbounded number of points on a circle.
  If and only if $2\pi/\rho$ is rational, the projection onto
  the $XY$-plane will contain a finite number of points.
  Because $\pi$ is transcendental and irrational,
  $2\pi/\rho$ is rational if and only if $\rho = a\pi/b$, where $a$ and $b$ are integers
  and, \highlighttext{assume} without loss of generality, $a$ and $b$ are coprime.
  Since $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
  The number of points in the projection is $2b$ if $a$ is odd, and $b$ if $a$ is even.
  This polygon has at least 3 sides, since either $\rho$ is irrational or $b > a$, and therefore
  $b \geq 2$. If $a/b = 1/2$, the projection is a square, which has four sides. 
\end{proof}

\begin{theorem}
  Any optimal tetrahelix with a rail angle of magnitude less than $\pi$ has all three
  axes coincident.
  \label{thm:coincident}
\end{theorem}
\begin{proof}
  Case 1: Suppose that $\rho$ is zero.
  Each helix has zero curvature, that is, it is a straight line. These lines are eqivalent
  to some three degenerate helices with coincident axes, possibly with different radii, so long as there is a phase
  term in the defintion of the helix, as in \cref{eq:colored}. We later show the
  radii must be eqivalent.

  Case 2: Suppose that $\rho$ is positive but less than $\pi$.
  In this case, each rail helix has
  curvature. The projection of points in the $XY$ plane creates a figure
  guaranteed to have points on either side of any line through the axis of such
  a helix, because the figure is either an $n$-gon or a circle by \cref{lemma:ngon}.
  We show that the three helices share a common axis.

@@

  \Cref{fig:wobble} illustrates this situation. Like most diagrams, it is
  overspecific, in that the two circles are drawn of the same radius but we do not
  depend upon that in this proof.  The diagram represents the projection along the
  $z$-axis of a few points into the $XY$-plane.

@@

Now that we have shown that on any optimal tetrahelix the vertices
are on helices of the same axes and pitch, we see that the vertices 
of any optimal tetrahelix will lie on a cylinder, or a circle when the axis dimension
is projected out. Therefore, it is reasonable to now speak of the singular radius $r$
of a tetrahelix as the radius of the cylinder.
We can now go on to
the harder proof about where vertices occur along the $z$-axis.

 We show that, in fact, the vertices must be distributed in even thirds
 along the $z$-axis as they are in the regular BC helix.

>>>>

The Boerdijk-Coxeter helix\cite{coxeter1985simplicial} (BC helix) (see \cref{fig:closeup,fig:closeuporthog}), is
a face-to-face stack of tetrahedra that winds about a straight axis.
Architects, structural engineers, and roboticists are inspired
by and follow such regular mathematical models.
However, since they can also build structures and
machines from members of differing or even dynamically changing length, it is
useful to develop the mathematics of structures formed from tetrahedra
where \highlighttext{one relaxes} regularity.

@@

Buckminster Fuller called the BC helix a \emph{tetrahelix}\cite{fuller1982synergetics},
a term now commonly used. \highlighttext{This paper} reserves \emph{BC helix} to mean the purely
regular structure and use \emph{tetrahelix} to refer
to any structure isomorphic to the BC helix.

@@

Imagining \cref{fig:closeup} or \cref{fig:closeuporthog} as a static mechanical structure,
observe that it is useful to the mechanical engineer
because the structure is a mechanically strong, inherently rigid,
omni-triangulated space frame.
Then imagine that each static edge is replaced with an
actuator that can dynamically become shorter or longer in response to electronic control,
and the vertices are joints that support sufficient angular displacement
for this to be possible. An example of such a machine is a Tetrobot,
shown in \cref{fig:tetrobot}.

A BC helix does not rest stably on a plane. It is convenient to
be able to ``untwist'' it and to form a tetrahelix space frame that has a
flat planar surface. By making length changes in a certain way, a \highlighttext{tetrahelix untwists} to form a \emph{tetrabeam} which has planar faces
and has, for example, an equilateral triangular profile. This paper
develops the equations needed to untwist the tetrahelix. All math
developed here is available in JavaScript and demonstrated by an interactive
design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
\highlighttext{and a video\cite{readvideo}},
from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
are taken.

@@

\Cref{fig:series} displays a continuum of tetrahelices optimal in a \highlighttext{in the sense of being
as regular as possible},
which is the main result of this
paper. The closest helix is the BC helix, and the furthest
is the equitetrabeam, defined in \cref{sec:equitetrabeam} and \cref{fig:naming,fig:equitetrabeam}.

@@

However, a robot must move, and so it is interesting to consider the
transmutations of these regular geometries. Developing a functional
gait for our physical Tetrobot (the 7-Tet Glussbot) was in fact the motivation
for this work.
By changing only the length of only one third of the members,
\highlighttext{one} can dynamically untwist a physical Tetrobot
forming the Boerdijk-Coxeter configuration into the equitetrabeam which rests flat on the plane,
as shown in figs. \highlighttext{4 and} 5.

By untwisting the tetrahelix so that is has a planar surface resting on the ground,
each vertex touching the ground \highlighttext{becomes} a foot or pseudopod. A robot can thus
become a hexapod or $n$-pod Tetrobot, and the already well-developed approaches to
hexapod gaits may be applied to make the robot walk or crawl.

@@

\highlighttext{
The remainder of this  paper:
\begin{enumerate}
\item Provides a new formulation for the BC helix that is more natural for engineers,
\item Defines a concept of minimum maximum edge-length optimality and proves that all
    optimal tetrahelices are in fact triple helices,
\item Provides formulae for constructing optimal tetrahelices of different twists or for optimally
    transforming a
    robot from a twisted to a planar configuration,
\item Gives a formula for the inradius of an optimal tetrahelix,
\item Describes a completely planar tetrahlix (the \emph{equitetrabeam}) useful as
  a structural beam or for applying standard robot gaits to a tetrahedral robot, and
\item Discusses the continuum of optimal tetrahelices between the BC Helix and equitetrabeam.
\end{enumerate}
}

@@

\highlighttext{Engineers} would like to design nearly regular tetrahelices with a formula that
gives the vertices in space. Eventually, \highlighttext{this would be done}
by choosing the lengths of a small set of members.
In a space frame, this is a static design choice; in a Tetrobot, it is a
dynamic choice that can be used to twist the robot and/or exert linear or
angular force on the environment.

Ideally, \highlighttext{a simple formula would define} the vertices based on
any curvature or pitch we choose. It is a goal of
this paper to relate the Cartesian coordinate approach and the member-length approach to
generating a tetrahelix continuum.

H.S.M. Coxeter constructs the BC helix\cite{coxeter1985simplicial} as a repeated rotation and
translation of the tetrahedra by showing the
rotation is:
\begin{equation}
\theta_{bc} = \arccos(-2/3) 
\end{equation}
and the translation:
\begin{equation}
h_{bc} = 1/\sqrt{10}.
\end{equation}

@@

This formula defines a helix, but it is not any of the apparent helices, or \emph{rail} helices, of the
BC helix, but rather one that winds much more rapidly through all
vertices. To a designer of tetrahelices, it is more natural to think of
the three helices which are visually apparent, that is, those three
which are closely approximated by the outer edges or rails of
the BC helix. Think of each of these three rails as being a different color: red, blue, or yellow.
This situation is illustrated in \cref{fig:helixcomparison}, wherein the black helix represents that
generated by \cref{graycoxeter},
and the colored helices are generated by \cref{eq:colored}, below.

In order to develop the continuum of slightly irregular tetrahelices,
\highlighttext{a formula is needed}
 that gives us the vertices of just
one rail helix, denoted by color $c$ and integer vertex number $n$:
\[
(\forall n \in \mathbb{Z}, \forall c \in \{0,1,2\} : \vec{H}_{BCcolored}(n,c) = \vec{V}(3n +c)) .
\]

@@

Note, in \cref{railanglefig}, the $z$-axis travel for one rail edge is denoted by $d$. In \cref{graycoxeter} and  \cref{eq:colored}, the variable
$h$ is used for one third of the distance we name $d$. \highlighttext{The fact that $d = 3h$ is justified later}.
In this paper, we assume the length of a rail
is always $1$ as a simplification, except in proofs concerning rail length.
The rail length is a parameter in the JavaScript code in
\url{https://github.com/PubInv/tetrahelix/blob/master/js/tetrahelix_math.js} \cite{readtetrahelix}.

The $\vec{H}_{BCcolored}(n,c)$ formulation can be further clarified by rewriting directly in terms of the rail angle $\rho_{bc}$ rather than $\theta_{bc}$.
Intuitively, an expression where $c/3$ is multiplied by a $1/3$ rotation plus the rail angle $\rho$ \highlighttext{is sought}.
We expand 
the expressions $\theta_{bc}$ and $\rho_{bc}$ in \cref{eq:colored} and seek to isolate the term $c 2\pi/3 $.

@@

Thus, starting with the expression:
\begin{align*}
  c \theta_{bc} 
\end{align*}
introduce 3 into the denominator...
\begin{align*}
  (c/3)  (3 \theta_{bc}) 
\end{align*}
\highlighttext{seeking} $2\pi$ in the numerator, add canceling terms...
\begin{align*}
  (c/ 3) ((3 \theta_{bc} - 2 \pi)  + 2 \pi) 
\end{align*}
...and then use the definition of $\rho_{bc}$
\begin{align*}
  (c / 3) \rho_{bc}  + c 2 \pi /3 
\end{align*}
\highlighttext{to} finally obtain:
\begin{equation}
  c  ( \rho_{bc} +  2 \pi) /3  \text{.}
\end{equation}

@@

Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued).
\highlighttext{It can now be asserted that} in \cref{fig:helixcomparison} the black helix winds at
$\frac{3 \theta_{bc}}{\rho_{bc}} \approx 11.16 $ times the rate of a rail helix.

From this formulation it is easy to see that moving one vertex on a rail
($\vec{H}_{BCcolored}(n,c)$ to $\vec{H}_{BCcolored}(n+1,c)$ for any $n$ and $c$)
moves us $\rho_{bc}$ radians around a circle. Since:
$ \frac{2 \pi}{\rho_{bc}} \approx 10.16 $
there are approximately $10.16$ red, blue or yellow tetrahedra on one rail in a
complete revolution of the tetrahelix.

@@

The pitch is less than the number of tetrahedra because the tetrahedra
edges are not parallel to the axis of the tetrahelix.  It is a famous and interesting result
that the pitch is irrational. A BC helix never has two tetrahedra at
precisely the same orientation around the $z$-axis. However, this is
inconvenient to designers, who might prefer a rational pitch.
The idea of developing a rational period by arranging solid tetrahedra by relaxing
the face-to-face matching
has been explored\cite{sadler2013periodic}. 
\highlighttext{The next sections develop} slightly irregular edge lengths that support, for example,
a pitch of precisely 12
tetrahedra in one revolution which would allow an architect to
design a pleasing column having the top and bottom tetrahedra in the same relationship to the
viewer on both the capital and the basis.

@@

\highlighttext{
As engineers and roboticists it is desirable to design tetrahelices that
are slightly irregular that ``untwist'' the BC Helix in an optimal way.
For machines
made out of linear actuators with limited range of extension,
the best definition of optimality is to minimize the difference in
lengths between the shortest and longest members in the robot of a given radius.
By maintaining all lengths as close to the same ``regular'' length as possible,
such as the mean length of the actuator,
one retains the greatest possible freedom of motion for the robot.
}

\highlighttext{
This paper use the term \emph{tetrahelix} to mean any structure physically constructible of
vertices and finite edges which is isomorphic to the BC helix, but with possibly different edge lengths,
and in which the
vertices lie on three helices (red, blue, and yellow, or ($R,B,Y$)). 
Mathematically, this structure extends
without bound, although physical robots or variable geometry trusses will
be truncations of such a structure.
This idea is captured by a function $T$ that gives the length between any
two nodes that are connected, and undefined ($\perp$) when not connected :
$T(n_1,n_2) : \mathbb{Z} \times \mathbb{Z} \mapsto \mathbb{R} \cup \{\perp\} $.
To describe a physically realizable machine, the function $T$ representing a tetrahelix
is constrained:
$(\forall n_1,n_2 : T(n_1,n_2) > 0)$.
For a BC Helix, $(\forall x,y : T(x,y) \neq \perp \Rightarrow T(x,y) = 1)$.
}

\highlighttext{
The ratio of the longest member in a testrahelix to the shortest is:
\begin{equation}
R(T) = \frac{\max \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}{\min \{T(n_1,n_2) | n_1,n_2 \in \mathbb{Z} \}}
\label{eq:optdef}
\end{equation}
}

\highlighttext{
  The ratio of the BC Helix is 1: $ R(H_{BC}) = 1$.
  }
\highlighttext{
A \emph{triple helix} is three congruent helices that share an axis. The remainder of this
section proves that
optimal tetrahelices are in fact triple helices.
In stages, this section proves that the helices in optimal tetrahelices:
\begin{enumerate}
\item have the same pitch,
\item have parallel axes,
\item share the same axis,
\item have the same radius,
  \item have the same rail length,
  \item have axially equidistant vertices, and therefore
  \item are in fact triple helices.
\end{enumerate}
The formula for radius that optimizes the tetrahelix for a given rail angle
is the result of the \cref{sec:parameterizing}.
}

\begin{proof}
\highlighttext{  
Suppose that all three rails do not have the same pitch.
Let $n1$ be a node on a  shortest edge between
two rails. Let $n2$ be a node on a different rail.
Increasing the difference $\|n2-n1\|$, increasing edge lengths $T(n_1,n_2)$
without bound,
which is not physically realizable.
}

\highlighttext{  
  Similarly, if the axes are not parallel, for any length $\lambda$ there is an edge of $T(x,y)$
  such that $T(x,y) > \lambda$, which is not physical.
}
\end{proof}

\highlighttext{
\Cref{thm:pitchandparallel} justifies talking about the singular
\emph{pitch} of 
the optimal tetrahelix as the pitch of its three rail helices $(R,B,Y)$, even though there are
three such helices of equivalent pitch.
Since the axes of helices of any physical tetrahelix are parallel, take
them to be parallel to the $z$ axis. Define the radius of the tetrahelix:
\begin{multline*}
rad(T) = \text{the radius of the smallest cylinder} \\
\text{which contains all of nodes of the tetrahelix } T
\end{multline*}
Define a \emph{minimax edge-length optimal tetrahelix} or just an
\emph{optimal tetrahelix} to be a tetrahelix for which there exists
no other tetrahelix  of the same radius with lower ratio of longest edge length to
shortest edge length
\begin{equation}
  OPT(T) \equiv \neg (\exists S : R(S) < R(T) \wedge rad(S) = rad(T))
  \label{eq:optdef}
\end{equation}
}

\highlighttext{
\begin{lemma}
  A tetrahelix where all points lie on the same line is not optimal.
    \label{lemma:notpoint}
\end{lemma}
\begin{proof}
As a little lemma for the proof below, observe that a tetrahelix $T$ of zero radius, where
all points lie on the same line,
is not as optimal as a tetrahelix of a small radius. The edges between rails $(R,B,Y)$ will be
shorter than the rail edges, and moving them apart slightly to form $T'$ lengthens the between-edge
rails, improving the ratios, so $R(T') < R(T)$.
\end{proof}
}

In the proof, below, \highlighttext{it is} useful to consider projection diagrams that are the axial projection
of a tetrahelix onto the $XY$-plane. \Cref{fig:projectiondiagram,fig:wobble} are examples
of such a diagram.
\begin{lemma}
  If the rail angle $0 < \rho < \pi$ is a rational multiple of $\pi$, then the projection of
  edges in a helix of that rail angle  along the $z$-axis onto the $XY$-plane form a
  regular polygon of 3 or more sides, \highlighttext{otherwise} they fill in a complete circle.
  \label{lemma:ngon}
\end{lemma}
\begin{proof}
  All points lying on a helix projected along the axis lie on a circle in the $XY$-plane.
\highlighttext{(By \cref{lemma:notpoint}, the circle is not a simple point.)}
  Helices are periodic in the $z$ dimension modulo $2\pi$.
  If $2\pi/\rho$ is irrational, the projection onto the $XY$-plane will contain
  an unbounded number of points on a circle.
  If and only if $2\pi/\rho$ is rational, the projection onto
  the $XY$-plane will contain a finite number of points.
  Because $\pi$ is transcendental and irrational,
  $2\pi/\rho$ is rational if and only if $\rho = a\pi/b$, where $a$ and $b$ are integers
  and, \highlighttext{assume} without loss of generality, $a$ and $b$ are coprime.
  Since $\rho < \pi$, therefore $a < b$. Also, $\rho > 0$, therefore $a > 0$.
  The number of points in the projection is $2b$ if $a$ is odd, and $b$ if $a$ is even.
  This polygon has at least 3 sides, since either $\rho$ is irrational or $b > a$, and therefore
  $b \geq 2$. If $a/b = 1/2$, the projection is a square, which has four sides. 
\end{proof}

\begin{theorem}
  Any optimal tetrahelix with a rail angle of magnitude less than $\pi$ has all three
  axes coincident.
  \label{thm:coincident}
\end{theorem}
\begin{proof}
  Case 1: Suppose that $\rho$ is zero.
  Each helix has zero curvature, that is, it is a straight line. These lines are eqivalent
  to some three degenerate helices with coincident axes, possibly with different radii,
  so long as there is a phase
  term in the defintion of the helix, as in \cref{eq:colored}. \highlighttext{That the
  radii must be eqivalent is shown later}.

  Case 2: Suppose that $\rho$ is positive but less than $\pi$.
  In this case, each rail helix has
  curvature. The projection of points in the $XY$ plane creates a figure
  guaranteed to have points on either side of any line through the axis of such
  a helix, because the figure is either an $n$-gon or a circle by \cref{lemma:ngon}.

@@

  \Cref{fig:wobble} illustrates this situation. Like most diagrams, it is
  overspecific, in that the two circles are drawn of the same radius but \highlighttext{
    this proof does not depend on that.
  }
  The diagram represents the projection along the
  $z$-axis of a few points into the $XY$-plane.

@@

Now that \highlighttext{is proven} that on any optimal tetrahelix the vertices
are on helices of the same axes and pitch, \highlighttext{observe} that the vertices 
of any optimal tetrahelix will lie on a cylinder, or a circle when the axis dimension
is projected out. Therefore, it is reasonable to now speak of the singular radius $r$
of a tetrahelix as the radius of the cylinder.
\highlighttext{This allows }
the harder proof about where vertices occur along the $z$-axis.
